Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-30 appendix.tex
tex
sga->lga

\section{More Details Explained}

@@

\begin{enumerate}[noitemsep, label={Q.{\arabic*}}]
		%
	\item \ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
		term.  Is it possible to introduce any other triplet combinations among
		the six samples (\ie, three benign and three adversarial)?}\\
		%
		A: We have tried some other combinations, and they are either not
		effective, or causing negative effects.
		%
		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
		adversarial training loss
		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
		performance on benign examples, but will drastically reduce model
		robustness;
		%
		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
		%
		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
		%
		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
		on benign examples, but drastically reduce robustness.

@@

%
Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.
%
However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

@@

\section{Complete Table for Sec~4.1 Hardness Selection}

@@

	\item [M] manuscript notes on SGA.

@@

	\item [\xmark] can we learn a good destination distribution? | too
		complicated? not necessary currently.

>>>>

\section{More Technical Details}

@@

%\begin{enumerate}[noitemsep, label={Q{\arabic*}.}]
\begin{enumerate}[noitemsep]
		%
	\item \ul{\it There is only $L_\text{T}(\va, \tilde{\va}, \vp)$ in the ICS
		term.  Is it possible to introduce any other triplet combinations among
		the six samples (\ie, three benign and three adversarial)?}\\
		%
		A: We have tried some other combinations, and they are either not
		effective, or causing negative effects.
		%
		In particular, (1) adding $L_\text{T}(\va, \vp, \vn)$ on top of the
		adversarial training loss
		$L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn})$ can improve
		performance on benign examples, but will drastically reduce model
		robustness;
		%
		(2) $L_\text{T}(\vp, \tilde{\vp}, \va)$ \oo{is duplicated, not necessary.}
		%
		(3) $L_\text{T}(\va, \tilde{\va}, \tilde{\vn})$ no distinct difference.
		%
		(4) $L_\text{T}(\va, \vp, \tilde{\vn})$ leads to better performance
		on benign examples, but drastically reduce robustness.

@@

	\item Loss normalization with $u$?

	\item Hardware and software platform?

	\item Details of EST?

	\item Details of ACT?
%
Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.
%
However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

	\item Complete Table for Sec~4.1 Hardness Selection?

@@

\section{Miscellaneous}

\textbf{Societal Impact}.
%
As encouraged by the author guidelines, we briefly discuss the potential
societal impact of our work.
%
Adversarial attacks may raise security considerations on deep learning
applications, and hence may have negative impact.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact.
%
Besides, although adversarial training is not environment-friendly due to its
high training cost in GPU time, our study has significantly improved the
adversarial training efficiency compared to the previous works.

\textbf{Limitations}.
%
\begin{quote}

Considering the limitations of an approach is an important part of good
academic scholarship. While many high-quality CVPR papers thoroughly consider
and discuss limitations, CVPR 2022 aims to emphasize the importance of an
honest treatment of limitations. Authors are thus explicitly encouraged to
discuss limitations, ideally by creating a separate "Limitations" (sub-)section
in their papers.

Such discussion shall point out any strong assumptions and how robust the
results are to violations of these assumptions (e.g., independence assumptions,
noiseless settings, model well-specification, asymptotic approximations only
held locally). Authors need to reflect on how these assumptions might be
violated in practice and what the implications would be.

The discussion shall also reflect on the scope of their claims, e.g., if the
authors only tested their approach on a few datasets or did a few runs. In
general, empirical results often depend on implicit assumptions, which should
be articulated. The discussion shall reflect on the factors that influence the
performance of the approach. For example, a recognition algorithm may perform
poorly when image resolution is low or images are taken in low lighting.

We understand that authors might fear that complete honesty about limitations
might be used by reviewers as grounds for rejection. It is worth keeping in
mind that a worse outcome might be if reviewers discover limitations that are
not acknowledged in the paper. In general, we advise authors to use their best
judgement and recognize that individual actions in favor of transparency play
an important role in developing norms that preserve the integrity of the
community. Reviewers will be specifically instructed to not penalize honesty
concerning limitations

\end{quote}

@@

	\item [M] manuscript notes on LGA.

@@
